---
title: "My First Report"
author: "Kyle Fernandez"
format:
  html:
    embed-resources: true
    pdf: default
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- Add a sentence here describing what you notice in the chart.
- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## My Notes

- What I learned today in class

```{r}
summary(patients)
```

- I learned that to run R, I can highlight the code on my .qmd file and press Shift + Return to run it. The output shows up in my Terminal.
- I also learned that, to render HTML, one way to do so is to right-click the .html file --> click "Download" --> open the downloaded file. This shows up as the pretty, rendered, document in a new tab on my browser. 

## One Small Calculation

```{r}
3+3
```


